---
title: "10-import"
output: html_notebook
---

## Importing the libraries:
```{r Importing the libraries}
library(tidyverse)
library(janitor)
library(readr)
library(assertr)
library(ggplot2)
library(corrplot)
library(ggcorrplot)
library(caret)
library(ranger)
library(randomForest)
library(ROCR)
library(e1071)
library(pROC)
library(Hmisc)
library(stats)
library(factoextra)
library(gridExtra)
library(cluster)
```

## Importing the dataset:
```{r Importing the dataset and checking the class column set}
BreastCancer <- read_csv("data/BreastCancer.csv")%>%
  assert(in_set("benign","malignant"), Class)
```

Applying clean_names funtion:
```{r Clean Names}
clean_names(BreastCancer)
```

<p> The dataset that I have choosen is the Breast Cancer Dataset. In this datsaet we have different attributes given which are related with the cancer type. We have been given the type of cancer i.e. Benign or Malignant according to the related rows.
The idea is to perform an exploratory analysis of the information contained in the dataset, figuring out ways of making the dataset tidier. The ultimate objective is to, in the end, build and compare models to predict if a given tumor is benign or malignant (breast cancer) using the information available on this dataset. <br>
Source: https://archive.ics.uci.edu/ml/datasets/breast+cancer+wisconsin+(original)
</p>

## Let's check some boundations and values for the dataset .... 

```{r Verifying Id column to have NA and unique values }
BreastCancer %>%
  verify(not_na(Id)) %>%
  verify(is_uniq(Id))
```

As we can see in above that test failed 100 times. <br>
Reason: As test is to be done on both so a subbject can have 2 same id's. <br>

Let's test NA values and bounds of Cl.thickness:
```{r testing NA values and bounds in Cl.thickness}
BreastCancer %>%
  assert(within_bounds(1,10),Cl.thickness) %>%
  verify(not_na(Cl.thickness))
```

As we can see above, our test passed, so there are no NA values in the Cl.thickness and the values are in the bounds of 1 and 10. <br>
 
Let's test NA values and bounds of Cell.size:
```{r testing NA values and bounds in Cell.size}
BreastCancer %>%
  assert(within_bounds(1,10),Cell.size) %>%
  verify(not_na(Cell.size))
```

As we can see above, our test passed, so there are no NA values in the Cell.size and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Cell.shape:
```{r testing NA values and bounds in Cell.shape}
BreastCancer %>%
  assert(within_bounds(1,10),Cell.shape) %>%
  verify(not_na(Cell.shape))
```

As we can see above, our test passed, so there are no NA values in the Cell.shape and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Marg.adhesion:
```{r testing NA values and bounds in Marg.adhesion}
BreastCancer %>%
  assert(within_bounds(1,10),Marg.adhesion) %>%
  verify(not_na(Marg.adhesion))
```

As we can see above, our test passed, so there are no NA values in the Marg.adhesion and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Epith.c.size:
```{r testing NA values and bounds in Epith.c.size}
BreastCancer %>%
  assert(within_bounds(1,10),Epith.c.size) %>%
  verify(not_na(Epith.c.size))
```

As we can see above, our test passed, so there are no NA values in the Epith.c.size and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Bare.nuclei:
```{r testing NA values and bounds in Bare.nuclei}
BreastCancer %>%
  assert(within_bounds(1,10),Bare.nuclei) %>%
  verify(not_na(Bare.nuclei))
```

As we can see above, our test passed for the bound to be in between 1 and 10 but failed for not_NA values. There are totla of 16 rows which contain NA values in Bare.nuclei.<br>

Let's test NA values and bounds of Bl.cromatin:
```{r testing NA values and bounds in Bl.cromatin}
BreastCancer %>%
  assert(within_bounds(1,10),Bl.cromatin) %>%
  verify(not_na(Bl.cromatin))
```
As we can see above, our test passed, so there are no NA values in the Bl.cromatin and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Normal.nucleoli:
```{r testing NA values and bounds in Normal.nucleoli}
BreastCancer %>%
  assert(within_bounds(0,10),Normal.nucleoli) %>%
  verify(not_na(Normal.nucleoli))
```
As we can see above, our test passed, so there are no NA values in the Normal.nucleoli and the values are in the bounds of 1 and 10.<br>

Let's test NA values and bounds of Mitoses:
```{r testing NA values and bounds in Mitoses}
BreastCancer %>%
  assert(within_bounds(0,10),Mitoses) %>%
  verify(not_na(Mitoses))
```

As we can see above, our test passed, so there are no NA values in the Mitoses and the values are in the bounds of 1 and 10.<br>

Let's test NA values for Class:
```{r testing NA values in Class}
BreastCancer %>%
  verify(not_na(Class))
```

As we can see above, our test passed, so there are no NA values in the Class.<br>

So, From testing certain bounds and NA values in the datset we found out that there are total of 16 rows where Bare.Nuclei is NA.<br>

We can either remove those NA values to clean the dataset or we can use Capping or Windsorisation technique (feature engineering technique) to fill those values.<br>
Let's explore more about the dataset to find outliers and if there are any, find out the way to deal with them.<br>










