---
title: "20-explore"
output: html_notebook
---


## Exploratory Data Analysis:

Let's find out how many Class values are in the dataset:
```{r Count of Class}
BreastCancer %>%
  ggplot(aes(x = Class,)) + 
  geom_bar(fill = "steelblue", color = "black")+ 
  geom_text(stat = "Count", aes(label = ..count..), vjust = -0.4)+
  labs(title = "Barplot of Breast_Cancer Dataset Class Column", x = "Class", y = "Count")+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

We fid that there are 2 Class (Benign and Malignant cancer) and there are total of 458 benign cancer records and 241 malignant records.

Let's find out about the outliers in the dataset on all parameters that are realted to cancer.
```{r Finding outliers in all columns that can help in predicting Cancer}
ggplot(stack(BreastCancer[,2:10]), aes(x = ind, y = values)) + 
  geom_boxplot(na.rm=T) + 
  labs(title = "Boxplots of Breast_Cancer Dataset Columns", x = "", y = "Values") + 
  scale_y_continuous(breaks = seq(1, 10, by = 1))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust=1)) 
```

We can infer from the above graph that several columns have outliers, with <b> Mitoses</b> having the most outliers. We can do feature engineering to remove those outliers.<br>
There are many ways to get rid of those outliers like--
<li> Capping </li>
<li> Windsorisation </li>
<li> Equal length discretisation </li> 






